Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-20 paper.qmd
MSE for different lwd values

mse_scurve_lwd <- ggplot(error_rm_scurve, 
                     aes(x = benchmark_rm_lwd, 
                         y = MSE)) + 
  geom_point(
    size = 1
    ) +
  geom_line(
    linewidth = 0.3
    ) + 
  # geom_vline(xintercept = benchmark1, linetype="solid", 
  #            color = "#bdbdbd", linewidth=1, alpha = 0.5) +
  scale_x_continuous("standardized bin count", 
         transform = "reverse") + 
  ylab("MSE") +
  ggtitle("(c)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, 
            angle=90),
        plot.title = element_text(size = 12))
```

@@

b1_m_scurve + mse_scurve_b + b1_m_scurve2 + 
mse_scurve_lwd + 
distance_hist + plot_layout(ncol=2)
```

>>>>

mse_scurve_lwd <- ggplot(error_rm_scurve, 
                     aes(x = benchmark_rm_lwd, 
                         y = MSE)) + 
  geom_point(
    size = 1
    ) +
  geom_line(
    linewidth = 0.3
    ) + 
  # geom_vline(xintercept = benchmark1, linetype="solid", 
  #            color = "#bdbdbd", linewidth=1, alpha = 0.5) +
  scale_x_continuous("standardized bin count", 
         transform = "reverse") + 
  ylab("MSE") +
  ggtitle("(c)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, 
            angle=90),
        plot.title = element_text(size = 12))

mse_scurve_lwd2 <- error_rm_scurve |>
  filter(b_non_empty >= 5) |>
  ggplot(aes(x = b_non_empty,y = MSE)) + 
  geom_point(
    size = 1
    ) +
  geom_line(
    linewidth = 0.3
    ) + 
  # geom_vline(xintercept = benchmark1, linetype="solid", 
  #            color = "#bdbdbd", linewidth=1, alpha = 0.5) +
  scale_x_continuous("m (b1 = 11)") + 
  ylab("MSE") +
  ggtitle("(e)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, 
            angle=90),
        plot.title = element_text(size = 12))
```

@@

b1_m_scurve + mse_scurve_b + b1_m_scurve2 + 
mse_scurve_lwd + mse_scurve_lwd2 +
distance_hist + plot_layout(ncol=2)
```
